---
title: "Practical Machine Learning Assignments"
author: "Kazuo Tamaru"
date: "22/2/2015"
output: html_document
---

### Our Goal
The goal of our project is to predict the manner in which participants did the exercise.  

###1.Load library & Get data
```{r, message = FALSE} 
library(caret)
library(randomForest)
training_URL <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
test_URL <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
training <- read.csv(training_URL, na.strings = c("NA", "", "#DIV/0!"))
testing <- read.csv(test_URL, na.strings = c("NA", "", "#DIV/0!"))
```

###2.Data Cleaning  
Following variables are excluded from the analysis.  
 (1)Variables related to time and user information(column 1:6).  
 (2)Variables with at least one “NA”. 
```{r}
training <- training[, -c(1:6)]
testing <-testing[, -c(1:6)]
NoNA <- apply(training, 2, function(x) !any(is.na(x)))
training <- training[ ,NoNA]
testing <- testing[ ,NoNA]
dim(training)
```

###3.Partitioning and Prediction
(1)We partition a 50% training set and a 50% test set.  
(2)We use caret with randomForest as our model with 5 fold cross validation.
```{r}
set.seed(24)
inTrain <- createDataPartition(y = training$classe, p = 0.005, list = FALSE)
Train <- training[inTrain, ]
Test <- training[-inTrain, ]
Model <- train(classe ~ ., data = Train, method="rf",
               trControl = trainControl(method = "cv", number = 5),
               prox = TRUE, allowParallel = TRUE)
Model
```

###4.Evaluating the Model
ConfusionMatrix is as follows.  
Accuracy is 99.6%. 95% Confidence Interval is (99.4%, 0.99.7%).
```{r}
confusionMatrix(predict(Model, newdata = Test), Test$classe)
```

###5.Predict classe
ConfusionMatrix is as follows.  
Accuracy is 99.6%. 95% Confidence Interval is (99.4%, 0.99.7%).
```{r}
predict(Model, newdata = testing)
```
